---
title: 'Data Analysis'
author: 
output: 
  github_document:
    toc: yes
  #pdf_document:
  #  dev: cairo_pdf
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

```{r "env", message=FALSE, warning=F}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
source(here::here("src/lib/functions.R"))
#renv::snapshot()
```

```{r "get data"}
load(here("data/raw-private/cleaned_data_w1.RData"))
df <- read_csv(here("data/raw-private/OpenQ_coded.csv"))
load(here("data/raw-private/cleaned_data_w4.RData"))
source(here("src/analysis/data_for_analysis_exp.R"))
save(d, file = here("data/intermediate/cleaned_experiment.RData"))
```

## Measurement Models -- Checks
```{r "measurement", fig.width=15, fig.height=8}
#source(here("src/analysis/measurementmodels.R"))
source(here("src/analysis/mm2.R"))
p1
p2
p1 + p2 +  plot_layout(widths = c(2, 1))
```

```{r "corr", fig.width=8, fig.height=8}
p3
```

## Measurement Models -- Fig. 1 in paper
```{r "corr-concepts", fig.width=8, fig.height=8}
dc <- cor(tmp[sapply(tmp,is.numeric)]) %>% 
  reshape2::melt() %>% 
  #filter(Var1 == "Populist Attitudes" & Var2 != "Populist Attitudes") %>% 
  mutate(value = round(value, 2)) 

ggplot(dc, aes(x = Var1, y = Var2, 
               fill = value, label = value)) +
  geom_tile( alpha = .6) +
  geom_text(color = "white",fontface = "bold") +
  labs(x = " ",
       y = " ") +
  theme_ipsum() +
  scale_fill_gradient(low = fig_cols[6], high = fig_cols[1]) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        axis.text=element_text(size=15))

dc2 <- d1 |>  
  mutate_at(vars(starts_with("H1b_")),
            funs(recode(., 
                        `1` = 1,
                        `2` = 0,
                        `3` = 0))) %>% 
  mutate(ideo = E2,
         rn = (H1b_4 + H1b_5 + H1b_7 + H1b_8 + H1b_10)/5,
         pn = ( H1b_3 + H1b_6 + H1b_9)/3,
         progn = (H1b_1 + H1b_2 + H1b_11)/3) %>% 
  dplyr::select(`Ideology` = ideo, 
                `Reluctant Nostalgia` = rn, 
                `Playful Nostalgia` = pn,
                `Progressive Nostalgia` = progn) %>% 
  drop_na() 

dc2 <- cor(dc2[sapply(dc2,is.numeric)]) %>% 
  reshape2::melt() %>% 
  #filter(Var1 == "Populist Attitudes" & Var2 != "Populist Attitudes") %>% 
  mutate(value = round(value, 2)) 

ggplot(dc2, aes(x = Var1, y = Var2, 
               fill = value, label = value)) +
  geom_tile( alpha = .6) +
  geom_text(color = "white",fontface = "bold") +
  labs(x = " ",
       y = " ") +
  theme_ipsum() +
  scale_fill_gradient(low = fig_cols[6], high = fig_cols[1]) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1),
        axis.text=element_text(size=15))
```

## Types of Nostalgia
```{r "open-q", fig.width=12, fig.height=12}
source(here("src/analysis/openQ.R"))
p1
ttest

check <- df %>% 
  filter(youth==1) %>% 
  pivot_longer(cols = anti_eu:colonialism) %>% 
  filter(value == 1)

paste0(round(dim(check)[1]/dim(df)[1]*100,2), "% of people feeling both individually and collectively nostalgic")
save(ds1, file = here("data/intermediate/cleaned_obs_data.RData"))
```

```{r "open-q2", fig.width=12, fig.height=8}
p2
```

## Figure 2
```{r "nost-ideo", fig.width=12, fig.height=12}
p2b
```

```{r "descr", fig.width=12, fig.height=12}
source(here("src/analysis/decr_nostalgia_types.R"))
p1
p2
p3
p4
```

## Experiment 

```{r "treatment-view", fig.width=12, fig.height=6, eval=T}
d <- d %>% 
  mutate(treatment = ifelse(scapegoat == 0 & nostalgia == 0, "No Nostalgia, No Scapegoat", NA),
         treatment = ifelse(scapegoat == 0 & nostalgia == 1, "Nostalgia, No Scapegoat", treatment),
         treatment = ifelse(scapegoat == 1 & nostalgia == 0, "No Nostalgia, Scapegoat", treatment),
         treatment = ifelse(scapegoat == 1 & nostalgia == 1, "Nostalgia, Scapegoat", treatment),
         H18 = H18 - 1)
d %>% 
  dplyr::select(H18, treatment) %>% 
  group_by(treatment) %>% 
  ggplot(aes(x = treatment, y = H18)) +
  see::geom_violinhalf(fill = fig_cols[9], alpha = .4,
                       color = "white") +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "gray55") +
  labs(x = "", y = "Support for Message") +
  theme_ipsum() +
  theme(axis.text=element_text(size=15)) +
  coord_flip()
```


## H3: All voters will be more supportive of nostalgic messages than non-nostalgic messages

```{r "testing-h3", fig.width=8, fig.height=8, eval=T}
source(here("src/analysis/h3_exp.R"))
```


### Populist voters will be more supportive of messages that mention a scapegoat than non-populist voters.

```{r "testing-h1", fig.width=12, fig.height=6, eval=T}
source(here("src/analysis/h1_exp.R"))
```


##  Right-wing voters will be more supportive of nostalgic messages than left-wing voters

```{r "testing-h2", fig.width=12, fig.height=8, eval=T}
source(here("src/analysis/h2_exp.R"))
```

### Figure 4 in paper
```{r "viz-h3", fig.width=8, fig.height=10, eval=T}
h1 %>% 
  add_case(h2) %>% 
  add_case(h3) %>% 
  filter(y == "Support for Message") %>% 
  mutate(hyp = factor(hyp,
                      levels = c("Hypothesis 3",
                                 "Heterogeneous Treatment Effect"))) %>% 
  ggplot(aes(x = estimate, y = var,
             xmin = lower, xmax = upper,
             color = factor)) +
  geom_point(position = position_dodge(width = 0.5)) + 
  geom_errorbar(width = 0, position = position_dodge(width = 0.5)) +
  theme_ipsum() +
  labs(x = "Regression Estimates",
       y = "",
       caption = "Reference category: No Nostalgia, No Scapegoat") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray85") +
  #facet_wrap(vars(hyp), ncol = 2, scales = "free") +
    facet_grid(hyp ~ y, scales = "free") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.text=element_text(size=15))
```

```{r "viz-h3-dv2", fig.width=15, fig.height=10, eval=T}
h3 %>% 
  filter(y != "Support for Message") %>% 
  mutate(hyp = factor(hyp,
                      levels = c("Hypothesis 3",
                                 "Heterogeneous Treatment Effect"))) %>% 
 ggplot(aes(x = estimate, y = var,
             xmin = lower, xmax = upper,
             color = factor)) +
  geom_point(position = position_dodge(.5)) +
  geom_errorbar(position = position_dodge(.5), width = 0) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols) +
  labs(x = "Prediction Support for Message",
       y = "",
       caption = "Reference category: No Nostalgia, No Scapegoat") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray85") +
  facet_grid(. ~ y, scales = "free") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.text=element_text(size=15)) +
  guides(color=guide_legend(nrow=1,byrow=TRUE))
```


### Robustness

1. Exclude centrists

```{r "exclude-centrists"}
d_r <- d |> 
  filter(E2_2b != "center")

tidy(lm(H18 ~  treatment +
                ideology, d_r)) %>% 
  mutate(y = "Support for Message",
         upper = (estimate + (std.error * 1.56)),
         lower = (estimate - (std.error * 1.56))) |> 
  mutate(var = "Experimental Treatment",
         hyp = "Hypothesis 3",
         term = recode(term,
                         `treatmentNo Nostalgia, Scapegoat` = "No Nostalgia, Scapegoat",
                         `treatmentNostalgia, Scapegoat` = "Nostalgia, Scapegoat",
                         `treatmentNostalgia, No Scapegoat` = "Nostalgia, No Scapegoat"))|> 
  filter(term %in% c("No Nostalgia, Scapegoat", 
                     "Nostalgia, Scapegoat",
                     "Nostalgia, No Scapegoat")) |> 
  dplyr::select(factor = term,
                var,
                y,
                estimate,
                upper:lower, hyp) |> 
  ggplot(aes(x = estimate, y = var,
             xmin = lower, xmax = upper,
             color = factor)) +
  geom_point(position = position_dodge(width = 0.5)) + 
  geom_errorbar(width = 0, position = position_dodge(width = 0.5)) +
  theme_ipsum() +
  labs(x = "Regression Estimates",
       y = "",
       title = "Robustness: Regression without centrists", 
       caption = "Reference category: No Nostalgia, No Scapegoat") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray85") +
  #facet_wrap(vars(hyp), ncol = 2, scales = "free") +
  #facet_grid(hyp ~ y, scales = "free") +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        axis.text=element_text(size=15))


```